### 2018-11-25 chapters/3-results.tex
readability

Regularized logistic regression together with LPOCV was used to estimate the
prediction performance of models trained on extracted features. Following are
the results obtained when all features from a single image type were used and
also for the best selected features within image type
(Table~\ref{tab:auc_imagetype}). Moreover, performances of the models combining
features are presented in Table~\ref{tab:auc_combinations}.

>>>>

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Table~\ref{tab:auc_imagetype} contains the
results for models within each image type using all or top 1\% of the features.

Similar performance estimates of the models combining features from different
image types are presented in Table~\ref{tab:auc_combinations}.
